For Induction-Induction, Induction is Enough

### 2019-11-11 paper/paper.tex
notation section

>>>>

\subsection{Metatheory and Notation}

We work in intensional Martin-Löf type theory, equipped with the following features:
\begin{itemize}
  \item Predicative universes $\Set_i$. We usually omit level indices in this paper.
  \item Dependent functions, notated as $(x : A)\ra B$, or as $A \ra B$ when non-dependent.
  \item $\Sigma$-types, notated either as $(x : A)\times B$, or as $\sum\limits_{x} B$
        when we want to leave the type of the first projection implicit. We use $A
        \times B$ for non-dependent pairs.
  \item Intensional propositional equality as $t = u$, with $\refl : t = t$. In
    this paper, we use extensional notation, and do not write explicit
    transports over equalities. However, we occasionally indicate by
    $e_1,\dots,e_n \#t$ that $t$ is well-typed thanks to the equalities
    $e_1$,\dots,$e_n$.
  \item Uniqueness of identity proofs (UIP), expressing $(e : t = t)\ra e = \refl$.
  \item Function extensionality, expressing $((x : A) \ra f\,x = g\,x) \ra f = g$.

\end{itemize}
